---
title: <h2>Teaching</h2>
pagetitle: "Franziska Roscher"
---

<br>
<br>

#### Office Hours:

Upon request.


<br>
<br>

#### Past Teaching Experience:

Teaching Assistant for **"Introduction to Research Methods for Politics"** (POL-UA 850), Spring 2021.

Instructor: Prof. Anna Harvey.

<br>

Teaching Assistant for **"Thinking, Learning and Consciousness in Humans and Machines"** (NODEP-UA 158), Fall 2020.

Instructor: Prof. David Stasavage.

<br>

Course Assistant for **"Civil Liberties"** (POL-UA 332), Spring 2019.

Instructor: Prof. Christine Harrington.

<br>

Teaching Assistant for **"Introduction to International Politics"** (POL-UA 700), Fall 2018.

Instructor: Prof. Shanker Satyanath.

<details>
<summary>Downloads</summary>
<p>
```{r,echo=F,message=F,warning=F}
xfun::pkg_load2(c("htmltools", "mime"))
xfun::embed_file('downloads/PBE Exercises.pdf', text ="PBE Exercises")
```
</p>
<p>
```{r,echo=F,message=F,warning=F}
xfun::pkg_load2(c("htmltools", "mime"))
xfun::embed_file('downloads/Exam Prep Exercises.pdf', text ="Exam Prep Exercises")
```
</p>
</details>



